ForOpenCL: Transformations Exploiting Array Syntax in Fortran for Accelerator Programming

### 2011-12-09 papers/IJCSE/foropencl.tex
edits
fixed (?) bibliography
edits to anonymize and put abstract in correct place

%\usepackage{natbib, stfloats}
\usepackage{cite}
\usepackage{graphicx}
%\usepackage[cmex10]{amsmath}
%\usepackage{amssymb}
%\usepackage{array}
\usepackage{url}
\usepackage{listings}

@@

\LRH{M. Sottile et~al.}

@@

% 1st. author
\authorA{Matthew J. Sottile}
\affA{Galois, Inc.\\
% Portland, OR 97204\\
 E-mail: mjsottile@computer.org}

% 2nd. author
\authorB{Craig E Rasmussen}
\affB{Los Alamos National Laboratory\\
% Los Alamos, NM 87545\\
 E-mail: crasmussen@lanl.gov}

% 3rd. author
\authorC{Wayne N. Weseloh}
\affC{Los Alamos National Laboratory\\
% Los Alamos, NM 87545\\
 E-mail: weseloh@lanl.gov}

% 4th. author
\authorD{Robert W. Robey}
\affD{Los Alamos National Laboratory\\
% Los Alamos, NM 87545\\
 E-mail: brobey@lanl.gov}

% 5th. author
\authorE{Daniel Quinlan}
\affE{Lawrence Livermore National Laboratory\\
% Livermore, CA 94550\\
 E-Mail: dquinlan@llnl.gov}

% 6th. author
\authorF{Jeffrey Overbey}
\affF{University of Illinois at Urbanna-Champaign\\
% Champaign, IL 61820\\
 E-mail: overbey2@illinois.edu}

%% bio
\begin{bio}
M. Sottile completed his PhD in 2006 from the University of New Mexico
from the Department of Electrical and Computer Engineering.  He is
presently working as a researcher at Galois, Inc. in Portland, Oregon
leading research work efforts in scientific and high performance computing.
His research interests include programming languages, compilation techniques,
computational physics and applied mathematics.

\noindent Craig has a bio.

\noindent Wayne has a bio.

\noindent Bob has a bio.

\noindent Dan has a bio.

\noindent Jeff has a bio.
\end{bio}

@@

%\bibliographystyle{abbrv}
\bibliographystyle{plain}
\bibliography{foropencl}

>>>>

\usepackage{natbib, stfloats}
\usepackage{cite}
\usepackage{graphicx}
%\usepackage[cmex10]{amsmath}
%\usepackage{amssymb}
%\usepackage{array}
\usepackage{url}
\usepackage{listings}

@@

%% ANONYMIZED
%\LRH{M. Sottile et~al.}
\LRH{ }

@@

%% ANONYMIZED
\authorA{Author names removed for review}
% 1st. author
%\authorA{Matthew J. Sottile}
%\affA{Galois, Inc.\\
% Portland, OR 97204\\
% E-mail: mjsottile@computer.org}

% 2nd. author
%\authorB{Craig E Rasmussen}
%\affB{Los Alamos National Laboratory\\
% Los Alamos, NM 87545\\
% E-mail: crasmussen@lanl.gov}

% 3rd. author
%\authorC{Wayne N. Weseloh}
%\affC{Los Alamos National Laboratory\\
% Los Alamos, NM 87545\\
% E-mail: weseloh@lanl.gov}

% 4th. author
%\authorD{Robert W. Robey}
%\affD{Los Alamos National Laboratory\\
% Los Alamos, NM 87545\\
% E-mail: brobey@lanl.gov}

% 5th. author
%\authorE{Daniel Quinlan}
%\affE{Lawrence Livermore National Laboratory\\
% Livermore, CA 94550\\
% E-Mail: dquinlan@llnl.gov}

% 6th. author
%\authorF{Jeffrey Overbey}
%\affF{National Center for Supercomputing Applications\\
% Champaign, IL 61820\\
% E-mail: overbey2@illinois.edu}

%% bio
%\begin{bio}
%M. Sottile completed his PhD in 2006 from the University of New Mexico
%from the Department of Electrical and Computer Engineering.  He is
%presently working as a researcher at Galois, Inc. in Portland, Oregon
%leading research work efforts in scientific and high performance computing.
%His research interests include programming languages, compilation techniques,
%computational physics and applied mathematics.

%\noindent Craig has a bio.

%\noindent Wayne has a bio.

%\noindent Bob has a bio.

%\noindent Dan has a bio.

%\noindent Jeff has a bio.
%\end{bio}

@@

%\bibliographystyle{abbrv}
\newcommand{\newblock}{}
\bibliographystyle{plainnat}
\bibliography{foropencl}
